Probability

### 2016-04-24 prob.tex
prob.tex \section{Quantum Probability Spaces} update comments...

The equalivance between 2. and 3. can be found
in Proposition 4.1.1 in \cite{Swart2013}. Notice that this proposition
holds for every dimension... So it is not exactly Gleason's theorem,
or at least not the main part of the Gleason's theorem...}

>>>>

The equalivance between 2. and 3. can be found in Proposition 4.1.1
in \cite{Swart2013}. Here, the Born rule~$\mu_{\psi}(E)$ is replaced
by a faithful pseudotrace $\tau$ and $\mu_{\psi}(E)=\tau\left(\proj{\psi}E\right)$.
The faithful pseudotrace is defined in section 5.2 Decomposition of
algebra with a list of conditions. The problem is:
\begin{itemize}
\item Lemma 5.2.1 proved there exists a faith pseudotrace, but said nothing
about uniqueness. Therefore, these conditions may not uniquely determine
the Born rule?
\item We don't formulate thing in algrebra... So although we may have an
analog or something, we cannot quite sure our conditions will be exactly
the same as theirs. 
\end{itemize}
If we admit the above, then the condition (a) to (c) and $\tau\left(AB\right)=\tau\left(BA\right)$
implies 
\begin{itemize}
\item Our map $\tilde{\mu}:\Hilb\rightarrow\qevents\rightarrow[0,1]$ should
satisfy $\tilde{\mu}_{\psi}$ is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
\end{itemize}
The condition (a) and (d) implies
\begin{itemize}
\item Our map $\tilde{\mu}$ satisfy $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
is impossible for $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $. 
\end{itemize}
$\tau\left(AB\right)=\tau\left(BA\right)$ also implies
\begin{itemize}
\item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
Besides, the condition (a) also gives the probability of mixed states
form pure states... OK... it seems that I know what I am going to
type for DQT, but I think I need to sort them out before type them...}
